The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
mv figures all to bottom
dont let figures into references
add most of missing refs

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social association
represents shared space use by members of the same social group [Figure
\@ref(fig:spacetime), @Franks_2009]. <!--Figure \@ref(fig:spacetime) TODO:
something broken here?? --> Further, for social interactions or associations to
occur individuals must share space, and thus have overlapping home ranges
[@VanderWal_2014]. In the context of the social environment, home range overlap
is an example of how animals share space over coarser spatial and temporal
scales (e.g. Piza-Roca et al. 2018). Although the social environment clearly
scales spatially and temporally, it remains unclear whether coarser scales of
sociality, including social association and home range overlap, vary predictably
with social interaction [@Castles_2014;
@Farine_2015a]. Thus, we define social scale as the type of social relationship
observed that can be explicitly defined and measured [@Farine_2015a]. <!--
Farine references comes out as D.R. Farine 2015 -->

@@

Given the existing framework for constructing multilayer networks from
behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicity
quantify movement paramters could be itnegrated. For example, edges could
represent measures of dyadic or collective movement based on dynamic interaction
metrics [@Long_2014]. Integrating movement layers with habitat-specific social
association layers could further illuminate the role of movement as a driver
of the social and spatial environments an individual experiences [@Webber_2018].
In our case study, we generated multilayer networks based on habitat-specific
monolayers. Coordinated movement of dyads, or groups, could vary based on
habitat, and the approach we outline could be used to explore mechanisms linking
the social and spatial environments. For example, social processes may be an
emergent property of the landscape because animals aggregate at resources, such
as waterholes [@Chamaillé_Jammes_2008]. Movement to, from, or within habitat
patches or territories can also contribute to the formation of the social
environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
males interacted primarily at home range edges, presumably driving territorial
behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
network framework is a logical next step for a burgeoning field. In particular,
when association networks are habitat-specific, we suggest the integration of
movement and space use in multilayer networks provides novel insights into the
effects of habitat configuration on the formation of the social environment
[@He_2019; @Webber_2018].

@@

The emergent relationship between habitat and sociality has been explored by the
distribution and phenology of resources and use of social information. Cougar
(*Puma concolor*) home ranges overlapped more in regions with high hunting
opportunity, a proxy for resource richness [@Elbroch_2016]. Caribou (*Rangifer
tarandus*) sociality differed between seasons, where social associations were
stronger in winter and contrastingly low in summer when resource availability
are more homogenous [@Peigner_2019]. Bison (*Bison bison*) showed stronger
habitat selection in larger groups and avoidance of predation risk was a main
factor contributing to their habitat selection [@Fortin_2009]. These examples,
comparing sociality and habitat selection across temporal or spatial contexts,
are implicitly multilayer analyses.

@@

>>>>

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social association
represents shared space use by members of the same social group [Figure
\@ref(fig:spacetime), @Franks_2009]. <!--Figure \@ref(fig:spacetime) TODO:
something broken here?? --> Further, for social interactions or associations to
occur individuals must share space, and thus have overlapping home ranges
[@Vander_Wal_2013]. In the context of the social environment, home range overlap
is an example of how animals share space over coarser spatial and temporal
scales (e.g. Piza-Roca et al. 2018). Although the social environment clearly
scales spatially and temporally, it remains unclear whether coarser scales of
sociality, including social association and home range overlap, vary predictably
with social interaction [@Castles_2014;
@Farine_2015a]. Thus, we define social scale as the type of social relationship
observed that can be explicitly defined and measured [@Farine_2015a]. <!--
Farine references comes out as D.R. Farine 2015 -->

@@

Given the existing framework for constructing multilayer networks from
behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicity
quantify movement paramters could be itnegrated. For example, edges could
represent measures of dyadic or collective movement based on dynamic interaction
metrics [@Long_2014]. Integrating movement layers with habitat-specific social
association layers could further illuminate the role of movement as a driver
of the social and spatial environments an individual experiences [@Webber_2018].
In our case study, we generated multilayer networks based on habitat-specific
monolayers. Coordinated movement of dyads, or groups, could vary based on
habitat, and the approach we outline could be used to explore mechanisms linking
the social and spatial environments. For example, social processes may be an
emergent property of the landscape because animals aggregate at resources, such
as waterholes [@Chamaill_Jammes_2008]. Movement to, from, or within habitat
patches or territories can also contribute to the formation of the social
environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
males interacted primarily at home range edges, presumably driving territorial
behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
network framework is a logical next step for a burgeoning field. In particular,
when association networks are habitat-specific, we suggest the integration of
movement and space use in multilayer networks provides novel insights into the
effects of habitat configuration on the formation of the social environment
[@He_2019; @Webber_2018].

@@

The emergent relationship between habitat and sociality has been explored by the
distribution and phenology of resources and use of social information. Cougar
(*Puma concolor*) home ranges overlapped more in regions with high hunting
opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou (*Rangifer
tarandus*) sociality differed between seasons, where social associations were
stronger in winter and contrastingly low in summer when resource availability
are more homogenous [@Peignier_2019]. Bison (*Bison bison*) showed stronger
habitat selection in larger groups and avoidance of predation risk was a main
factor contributing to their habitat selection [@Fortin_2009]. These examples,
comparing sociality and habitat selection across temporal or spatial contexts,
are implicitly multilayer analyses.

@@

\newpage
\clearpage
